---
title: "Homework4"
author: "LIU Aoran"
date: "2024-04-19"
output: pdf_document
---

Full name: LIU Aoran

Preferred name: Aaron

ID: 29246040

```{r eval=FALSE}
install.packages("dplyr")
install.packages("knitr")
install.packages("kableExtra")
install.packages("jtools")
```
```{r}
library(dplyr)
library(knitr)
library(kableExtra)
library(jtools)
```

# Task 1

To download the palmerpenguins package from CRAN, I used the install.packages() function.

```{r eval=FALSE}
# Install the package if necessary
install.packages("palmerpenguins")
```

I do not want to execute this code in your R Markdown file for the reason that:

1. Repeatedly installing the package every time knit the document can be time-consuming and unnecessary.
2. The code to install packages is typically a one-time setup task, not something should to be repeated every time when render the document. 

# Task 2

```{r}
library(palmerpenguins)
?palmerpenguins
variable_names <- names(penguins)
print(variable_names)
str(penguins)
```

The palmerpenguins data contains size measurements for three penguin species observed on three islands in the Palmer Archipelago, Antarctica. The package contains two datasets: `penguins` and `penguins_raw`. The most commonly used dataset is penguins, which contains data on three species of penguins (`Adelie`, `Chinstrap`, and `Gentoo`) from three islands (`Torgersen`, `Biscoe`, and `Dream`) in the Palmer Archipelago.

The curated palmerpenguins::penguins dataset contains 8 variables: `r paste(variable_names, collapse = ", ")`.

Based on the output of the str() function, we can see that the species variable is a factor, bill length and depth are numeric, and so on.

# Task 3 & 4

```{r}
# Find distinct values of the species variable using dplyr's distinct() function
distinct_species <- palmerpenguins::penguins |> 
    distinct(species)

# Convert the distinct species to a character vector
species_vector <- as.character(distinct_species$species)

print(species_vector)
```

The distinct species in the dataset are: `r paste(species_vector, collapse = ", ")`.

# Task 5

```{r}
# Find distinct values of the islands variable using dplyr's distinct() function
distinct_islands <- palmerpenguins::penguins |> 
    distinct(island)

# Convert the distinct islands to a character vector
islands_vector <- as.character(distinct_islands$island)

print(islands_vector)
```

The distinct species in the dataset are: `r paste(islands_vector, collapse = ", ")`.

# Task 6

Here is the function that accepts a data frame and performs a linear regression of the body_mass_g variable on the sex variable.
```{r}
regress_body_mass_on_sex <- function(data_frame) {
    # Perform the linear regression of body_mass_g on sex using lm()
    lm_model <- lm(body_mass_g ~ sex, data = data_frame)
    
    # Return the regression object (lm model)
    return(lm_model)
}


# Use the function to perform the regression on the penguins data frame
regression_result <- regress_body_mass_on_sex(palmerpenguins::penguins)

# Print the summary of the regression result
summ(regression_result)
```

# Task 7

```{r}
# Filter rows for the species "Adelie"
adelie_penguins <- penguins %>%
    filter(species == "Adelie")

# Filter rows for the species "Chinstrap"
chinstrap_penguins <- penguins %>%
    filter(species == "Chinstrap")

# Filter rows for the species "Gentoo"
gentoo_penguins <- penguins %>%
    filter(species == "Gentoo")
```

# Task 8

```{r}
# Regression for Adelie penguins
adelie_regression <- regress_body_mass_on_sex(adelie_penguins)

# Regression for Chinstrap penguins
chinstrap_regression <- regress_body_mass_on_sex(chinstrap_penguins)

# Regression for Gentoo penguins
gentoo_regression <- regress_body_mass_on_sex(gentoo_penguins)
```
```{r}
summ(adelie_regression)
summ(chinstrap_regression)
summ(gentoo_regression)
```

# Task 9 (The results)
```{r}
# Extract coefficients for each species
adelie_sex_coef <- summary(adelie_regression)$coefficients[2, 1]
chinstrap_sex_coef <- summary(chinstrap_regression)$coefficients[2, 1]
gentoo_sex_coef <- summary(gentoo_regression)$coefficients[2, 1]

```

1. The estimated coefficient for sex in Adelie penguins is `r adelie_sex_coef`.
2. The estimated coefficient for sex in Chinstrap penguins is `r chinstrap_sex_coef`.
3. The estimated coefficient for sex in Gentoo penguins is `r gentoo_sex_coef`.

The regression results show that:

1. For the male *Adelie penguins*, on average, weigh approximately `r adelie_sex_coef` grams more than female Adelie penguins. This suggests a significant level of sexual dimorphism in body mass within Adelie penguins, with males being notably heavier than females.
Chinstrap Penguins:
2. For the male *Chinstrap penguins*, on average, weigh approximately `r chinstrap_sex_coef` grams more than female Chinstrap penguins. This also suggests sexual dimorphism in body mass within Chinstrap penguins, with males being heavier than females.
3. For the male *Gentoo penguins*, on average, weigh approximately `r gentoo_sex_coef` grams more than female Gentoo penguins. This indicates the highest level of sexual dimorphism in body mass within Gentoo penguins compared to the other two species, with males being significantly heavier than females.
